String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-11 2023-1-19/sections/implementation.tex
experiments

Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL. The experimental results can be found in Table~\ref{tab:results_all}. From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solves 48,689 instances correctly, which is 3,982/2,263/24,568/12,823/1,082/7083\zhilin{xxx} more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Note that Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth. If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, OSTRICH$^{\rm RECL}$ is almost as fast as the fastest solver Z3str3RE. More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while Z3str3RE spends 1.71 seconds per instance, while the other solvers spend at least 3 seconds per instance.  
Z3-Trau reports ``unknown'' on 21,655 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.

>>>>

Q1 is answered by running OSTRICH$^{\rm RECL}$ and the aforementioned solvers on AutomatArk and RegCoL. The experimental results can be found in Table~\ref{tab:results_all}. From Table~\ref{tab:results_all}, we can see that OSTRICH$^{\rm RECL}$ solvers almost all 48,834 instances, except 144 of them, that is, it solves 48,689 instances correctly, which is 3,982/2,263/24,568/12,823/1,082/7083 more than the number of instances solved by CVC5/Z3seq/Z3-Trau/Z3str3/Z3str3RE/OSTRICH respectively. 
%    
Note that Z3seq, Z3-Trau, Z3str3, and Z3str3RE have soundness errors, where the result of CVC5 is taken as the ground truth. If CVC5 reports ``unknown'' or ``timeout'' in some instance, then no soundness errors will be reported in this instance. 
%A soundness error is reported if the result of a solver for an instance is different from CVC5. 
% their results on some instances are inconsistent with the results of the other three solvers, i.e. CVC5, OSTRICH, and OSTRICH$^{\rm RECL}$.
%
Moreover, OSTRICH$^{\rm RECL}$ is the second fastest solver. More specifically, OSTRICH$^{\rm RECL}$ spends 2.93 seconds per instance on average, while the fastest solver Z3str3RE spends 1.71 seconds per instance, and the other solvers spend at least 3 seconds per instance.  
Z3-Trau reports ``unknown'' on 21,655 instances, which is mainly attributed to the fact that it does not support \verb|re.diff|, the language difference operator of regular expressions.
